The Right Way to Search Evolving Graphs

### 2016-02-22 paper.tex
Remove table

We generate a group of  random (directed) \texttt{IntEvolvingGraph}s
with $8,000$ active nodes and $4$ time stamps.
At each time stamp $i$, an edge is included in $G^{[i]} \in G_4$ with probability $p$.
Figure \ref{fig:time} shows the plots of number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted
on a Linux system with Intel(R) Core(TM) i7-3537U CPU @ $2.00$GHz.

The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with Theorem \ref{thm:complexity}. A summary of the experiments is provided in Table \ref{tab:bfs}.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.44]{time.pdf}
  \caption{Experiments of running Algorithm \ref{alg:bfs}
on a group of random evolving graphs with $8,000$ active nodes and $4$ time stamps. The x-axis shows the
number of edges of each evolving graph and the y-axis shows the corresponding
computation time. The values in the x, y-axis increase linearly from left to
right and from bottom to top respectively.}
  \label{fig:time}
\end{figure}
\begin{table}[h]
\centering
\begin{tabular}{c | c | c | c }
\hline
probability $p$ & no. of edges  & time (s) &  memory (MB) \\\hline
      0.01  &         160,156      & 0.098   & 18.388  \\
      0.09  &       1,440,895        & 0.446  &  134.253  \\
      0.15   &     2,399,774         & 0.743 & 221.511 \\
      0.23   &    3,676,959          & 1.206 &   337.688 \\
      0.31   &     4,956,969          & 1.504  &  494.833 \\
\end{tabular}
\caption{the computation time and the amount of memory allocated for
computing Algorithm \ref{alg:bfs}. This is a summery of Figure \ref{fig:time}.
Each edge is included in the graph with probability $p$. }
\label{tab:bfs}
\end{table}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.

>>>>

We generate a group of random (directed) \texttt{IntEvolvingGraph}s
with $8,000$ active nodes and $4$ time stamps.
At each time stamp $i$, a static edge is included in $G^{[i]} \in G_4$ with
probability $p$. Note that in this experiment, we do not have direct control
over the full edge set $E$, only the static edge set $\tilde E$. However, the
causal edge set $E'$ can grow at most by $O(\tilde E)$, so it suffices to demonstrate
linear scaling in $|\tilde E|$.
Figure \ref{fig:time} shows the plots of number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted
on a Linux system with Intel(R) Core(TM) i7-3537U CPU @ $2.00$GHz.

The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with the result of Theorem \ref{thm:complexity}.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.44]{time.pdf}
  \caption{Experimental run time and memory use of Algorithm \ref{alg:bfs}
on a collection of random evolving graphs with $8,000$ active nodes and $4$ time
stamps, showing linear scaling in $|\tilde E|$. The horizontal axis shows the
number of edges ($|\tilde E|$, including both static and causal edges) of each evolving
graph, while the vertical axis shows the corresponding
computation time.}
  \label{fig:time}
\end{figure}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.
